Figures

### 2025-07-09 code/07_data_analysis.Rmd
No build, pushing to switch machines :D

intercept_lnRR<- rma.mv(yi = lnRR_sign, # specify lnRR as the effect size measure;
                    V = VCV_lnRR, # specify lnRR's sampling variance-covariance matrix;
                    mods = ~ 1,
                    random = list(~ 1 | paper_ID,
                                  ~ 1 | Observation_ID,
                                  ~ 1 | group_ID_coded,
                                  ~ 1 | population_ID,
                                  ~ 1 | bird_species),
                    method = "REML",
                    control = list(optimizer="optim"),
                    test = "t",
                    data = dataset_lnRR)
# saving the model
saveRDS(intercept_lnRR, file = here::here("model/intercept_lnRR.rds"))

# saving the dataset for this model
write.csv(dataset_lnRR,here::here("data/04_data_analysis/intercept_lnRR.csv"))
```

@@

# saving the model
saveRDS(intercept_SMDH, file = here::here("model/intercept_SMDH.rds"))

# saving the dataset for this model
write.csv(dataset_SMDH,here::here("data/04_data_analysis/intercept_SMDH.csv"))
```

@@

## For the lnRR effect size...
dataset_lnRR_no_comp3<-dataset_lnRR%>%filter(comparision_type!=3)
## Only some rows are removed... 
nrow(dataset_lnRR)-nrow(dataset_lnRR_no_comp3)

@@

dataset_SMDH_no_comp3<-dataset_SMDH%>%filter(comparision_type!=3)
## Only some rows are removed... 
nrow(dataset_SMDH)-nrow(dataset_SMDH_no_comp3)

@@

Results remain practically the same irrespective..

@@

```{r}
#----------------------------------------------------------------------------------
# For Different hypothesis
#----------------------------------------------------------------------------------

# lnRR_hypothesis_pc <-
#   metafor::rma.mv(yi = lnRR_sign, # specify lnRR as the effect size measure;
#                     V = VCV_lnRR,# specify lnRR's sampling variance;
#                     mods = ~ Hypothesis,
#                     random = list(~ 1 | paper_ID,
#                                   ~ 1 | Observation_ID,
#                                   ~ 1 | group_ID_coded,
#                                   ~ 1 | population_ID,
#                                   ~ 1 | bird_species),
#                     method = "REML",
#                   test = "t",
#                   control = list(optimizer="optim"),
#                   data = dataset_lnRR)
# 
# # I now want to test for statistical differences between groups. Male and fem
# # information for androgens can be obtained from the outcome of the table. For thyroid
# # hormones I need to do Post-hoc Wald tests: 
# car::linearHypothesis(lnRR_hypothesis_pc, rbind(c(0,1,-1)))
```

>>>>

intercept_lnRR<- rma.mv(yi = lnRR_sign, # specify lnRR as the effect size measure;
                    V = VCV_lnRR, # specify lnRR's sampling variance-covariance matrix;
                    mods = ~ 1,
                    random = list(~ 1 | paper_ID,
                                  ~ 1 | Observation_ID,
                                  ~ 1 | group_ID_coded,
                                  ~ 1 | population_ID,
                                  ~ 1 | bird_species),
                    method = "REML",
                    control = list(optimizer="optim"),
                    test = "t",
                    data = dataset_lnRR)
# saving the model
# saveRDS(intercept_lnRR, file = here::here("model/intercept_lnRR.rds"))

# saving the dataset for this model
# write.csv(dataset_lnRR,here::here("data/04_data_analysis/intercept_lnRR.csv"))
```

@@

# saving the model
# saveRDS(intercept_SMDH, file = here::here("model/intercept_SMDH.rds"))

# saving the dataset for this model
# write.csv(dataset_SMDH,here::here("data/04_data_analysis/intercept_SMDH.csv"))
```

@@

## For the lnRR effect size...
dataset_lnRR_no_comp3<-dataset_lnRR%>%filter(comparision_type!=3 | is.na(comparision_type))
## Only some rows are removed... 
nrow(dataset_lnRR)-nrow(dataset_lnRR_no_comp3)

@@

dataset_SMDH_no_comp3<-dataset_SMDH%>%filter(comparision_type!=3 | is.na(comparision_type))
## Only some rows are removed... 
nrow(dataset_SMDH)-nrow(dataset_SMDH_no_comp3)

@@

Overall conclusions remain practically the same irrespective.. now what about the meta-regression using Type of Experiment Design

dataset_lnRR_design_SA <- dataset_lnRR %>% filter(comparision_type!=3)

VCV_lnRR_design_SA <- vcalc(vi = lnRR_variance,
                  cluster = paper_ID,
                  obs = Observation_ID,
                  data = dataset_lnRR_design_SA,
                  rho = 0.5 # assuming that the effect sizes within the same study are correlated with rho = 0.5
                  )
lnRR_design_SA <-
  metafor::rma.mv(yi = lnRR_sign, # specify lnRR as the effect size measure;
                    V = VCV_lnRR_design_SA ,# specify lnRR's sampling variance;
                    mods = ~ - 1 + comparision_type,
                    random = list(~ 1 | paper_ID,
                                  ~ 1 | Observation_ID,
                                  ~ 1 | group_ID_coded,
                                  ~ 1 | population_ID,
                                  ~ 1 | bird_species),
                    method = "REML",
                  test = "t",
                  control = list(optimizer="optim"),
                  data = dataset_lnRR_design_SA )

## Now for SMDH

dataset_SMDH_design_SA <- dataset_SMDH %>% filter(comparision_type!=3)

VCV_SMDH_design_SA <- vcalc(vi = SMDH_variance,
                  cluster = paper_ID,
                  obs = Observation_ID,
                  data = dataset_SMDH_design_SA,
                  rho = 0.5 # assuming that the effect sizes within the same study are correlated with rho = 0.5
                  )
SMDH_design_SA <-
  metafor::rma.mv(yi = SMDH_sign, # specify lnRR as the effect size measure;
                    V = VCV_SMDH_design_SA ,# specify lnRR's sampling variance;
                    mods = ~ - 1 + comparision_type,
                    random = list(~ 1 | paper_ID,
                                  ~ 1 | Observation_ID,
                                  ~ 1 | group_ID_coded,
                                  ~ 1 | population_ID,
                                  ~ 1 | bird_species),
                    method = "REML",
                  test = "t",
                  control = list(optimizer="optim"),
                  data = dataset_SMDH_design_SA)
```

@@

```{r}
#----------------------------------------------------------------------------------
# For Different hypothesis
#----------------------------------------------------------------------------------
## For lnRR
VCV_lnRR<- vcalc(vi = lnRR_variance,
                  cluster = paper_ID,
                  obs = Observation_ID,
                  data = dataset_lnRR,
                  rho = 0.5 # assuming that the effect sizes within the same study are correlated with rho = 0.5
                  )

lnRR_hypothesis_pc <-
  metafor::rma.mv(yi = lnRR_sign, # specify lnRR as the effect size measure;
                    V = VCV_lnRR,# specify lnRR's sampling variance;
                    mods = ~ Hypothesis,
                    random = list(~ 1 | paper_ID,
                                  ~ 1 | Observation_ID,
                                  ~ 1 | group_ID_coded,
                                  ~ 1 | population_ID,
                                  ~ 1 | bird_species),
                    method = "REML",
                  test = "t",
                  control = list(optimizer="optim"),
                  data = dataset_lnRR)

# I now want to test for statistical differences between groups. Male and fem
# information for androgens can be obtained from the outcome of the table. For thyroid
# hormones I need to do Post-hoc Wald tests:
car::linearHypothesis(lnRR_hypothesis_pc, rbind(c(0,1,-1)))

# saving the model
saveRDS(lnRR_hypothesis_pc, file = here::here("model/lnRR_hypothesis_pc.rds"))

# For SMDH

SMDH_hypothesis_pc <-
  metafor::rma.mv(yi = SMDH_sign, # specify lnRR as the effect size measure;
                    V = VCV_SMDH,# specify lnRR's sampling variance;
                    mods = ~ Hypothesis,
                    random = list(~ 1 | paper_ID,
                                  ~ 1 | Observation_ID,
                                  ~ 1 | group_ID_coded,
                                  ~ 1 | population_ID,
                                  ~ 1 | bird_species),
                    method = "REML",
                  test = "t",
                  control = list(optimizer="optim"),
                  data = dataset_SMDH)

# I now want to test for statistical differences between groups. Male and fem
# information for androgens can be obtained from the outcome of the table. For thyroid
# hormones I need to do Post-hoc Wald tests:
car::linearHypothesis(SMDH_hypothesis_pc, rbind(c(0,1,-1)))
# saving the model
saveRDS(SMDH_hypothesis_pc, file = here::here("model/SMDH_hypothesis_pc.rds"))

#----------------------------------------------------------------------------------
# For Type of experimental design
#----------------------------------------------------------------------------------

# This analysis only includes dataset that has a proxy relating to comaparision type
dataset_lnRR_design <- dataset_lnRR %>% filter(!is.na(comparision_type))

VCV_lnRR_design <- vcalc(vi = lnRR_variance,
                  cluster = paper_ID,
                  obs = Observation_ID,
                  data = dataset_lnRR_design,
                  rho = 0.5 # assuming that the effect sizes within the same study are correlated with rho = 0.5
                  )
lnRR_design_pc <-
  metafor::rma.mv(yi = lnRR_sign, # specify lnRR as the effect size measure;
                    V = VCV_lnRR_design ,# specify lnRR's sampling variance;
                    mods = ~ comparision_type,
                    random = list(~ 1 | paper_ID,
                                  ~ 1 | Observation_ID,
                                  ~ 1 | group_ID_coded,
                                  ~ 1 | population_ID,
                                  ~ 1 | bird_species),
                    method = "REML",
                  test = "t",
                  control = list(optimizer="optim"),
                  data = dataset_lnRR_design )

# Saving the model
saveRDS(lnRR_design_pc, file = here::here("model/lnRR_design_pc.rds"))

VCV_SMDH_design <- vcalc(vi = SMDH_variance,
                  cluster = paper_ID,
                  obs = Observation_ID,
                  data = dataset_SMDH_design,
                  rho = 0.5 # assuming that the effect sizes within the same study are correlated with rho = 0.5
                  )
SMDH_design_pc <-
  metafor::rma.mv(yi = SMDH_sign, # specify lnRR as the effect size measure;
                    V = VCV_SMDH_design ,# specify lnRR's sampling variance;
                    mods = ~ comparision_type,
                    random = list(~ 1 | paper_ID,
                                  ~ 1 | Observation_ID,
                                  ~ 1 | group_ID_coded,
                                  ~ 1 | population_ID,
                                  ~ 1 | bird_species),
                    method = "REML",
                  test = "t",
                  control = list(optimizer="optim"),
                  data = dataset_SMDH_design )

# Saving the model
saveRDS(SMDH_design_pc, file = here::here("model/SMDH_design_pc.rds"))

#----------------------------------------------------------------------------------
# For Time of addition of GNM
#----------------------------------------------------------------------------------

## We use the complete dataset in this case
lnRR_time_gnm_addition_pc <-
  metafor::rma.mv(yi = lnRR_sign, # specify lnRR as the effect size measure;
                    V = VCV_lnRR,# specify lnRR's sampling variance using the variance-covariance matrix we created for the intercept-only model since the whole dataset is being used in this case as well
                    mods = ~ time_of_gnm_addition,
                    random = list(~ 1 | paper_ID,
                                  ~ 1 | Observation_ID,
                                  ~ 1 | group_ID_coded,
                                  ~ 1 | population_ID,
                                  ~ 1 | bird_species),
                    method = "REML",
                  test = "t",
                  control = list(optimizer="optim"),
                  data = dataset_lnRR)

## Saving the model
saveRDS(lnRR_time_gnm_addition_pc, file = here::here("model/lnRR_time_gnm_addition_pc.rds"))

## Now similarly for the SMDH effect size using the complete dataset
SMDH_time_gnm_addition_pc <-
  metafor::rma.mv(yi = SMDH_sign, # specify lnRR as the effect size measure;
                    V = VCV_SMDH,# specify lnRR's sampling variance using the variance-covariance matrix we created for the intercept-only model since the whole dataset is being used in this case as well
                    mods = ~ time_of_gnm_addition,
                    random = list(~ 1 | paper_ID,
                                  ~ 1 | Observation_ID,
                                  ~ 1 | group_ID_coded,
                                  ~ 1 | population_ID,
                                  ~ 1 | bird_species),
                    method = "REML",
                  test = "t",
                  control = list(optimizer="optim"),
                  data = dataset_SMDH)

## Saving the model
saveRDS(SMDH_time_gnm_addition_pc, file = here::here("model/SMDH_time_gnm_addition_pc.rds"))

#----------------------------------------------------------------------------------
# Parasite Type
#----------------------------------------------------------------------------------

# This analysis only includes dataset that has a proxy relating to parasite or pathogen
dataset_lnRR_parasite <- dataset_lnRR%>%
  filter(!is.na(parasite_type))%>%
  mutate(parasite_type=as.factor(parasite_type),
         paper_ID=as.factor(paper_ID),
         Observation_ID=as.factor(Observation_ID),
         group_ID_coded=as.factor(group_ID_coded),
         bird_species=as.factor(bird_species))

lnRR_parasite_pc <-
  metafor::rma.mv(yi = lnRR_sign, # specify lnRR as the effect size measure;
                    V = VCV_lnRR_parasite,# specify lnRR's sampling variance;
                    mods = ~ parasite_type,
                    random = list(~ 1 | paper_ID,
                                  ~ 1 | Observation_ID,
                                  ~ 1 | group_ID_coded,
                                  ~ 1 | population_ID,
                                  ~ 1 | bird_species),
                    method = "REML",
                   test = "t",
                  control = list(optimizer="optim"),
                  data = dataset_lnRR_parasite)

# Saving the model
saveRDS(lnRR_parasite_pc, file = here::here("model/lnRR_parasite_pc.rds"))

SMDH_parasite_pc <-
  metafor::rma.mv(yi = SMDH_sign, # specify lnRR as the effect size measure;
                    V = VCV_SMDH_parasite,# specify lnRR's sampling variance;
                    mods =  parasite_type,
                    random = list(~ 1 | paper_ID,
                                  ~ 1 | Observation_ID,
                                  ~ 1 | group_ID_coded,
                                  ~ 1 | population_ID,
                                  ~ 1 | bird_species),
                    method = "REML",
                   test = "t",
                  control = list(optimizer="optim"),
                  data = dataset_SMDH_parasite)

# Save the model
saveRDS(SMDH_parasite_pc, file = here::here("model/SMDH_parasite_pc.rds"))

#----------------------------------------------------------------------------------
# Bird Species
#----------------------------------------------------------------------------------

lnRR_birds_pc <-
  metafor::rma.mv(yi = lnRR_sign, # specify lnRR as the effect size measure;
                    V = VCV_lnRR,# specify lnRR's sampling variance;
                    mods = ~ bird_species,
                    random = list(~ 1 | paper_ID,
                                  ~ 1 | Observation_ID,
                                  ~ 1 | group_ID_coded,
                                  ~ 1 | population_ID,
                                  ~ 1 | bird_species),
                    method = "REML",
                  test = "t",
                  control = list(optimizer="optim"),
                  data = dataset_lnRR)

# Saving the model
saveRDS(lnRR_birds_pc, file = here::here("model/lnRR_birds_pc.rds"))

SMDH_birds_pc <-
  metafor::rma.mv(yi = SMDH_sign, # specify lnRR as the effect size measure;
                    V = VCV_SMDH,# specify lnRR's sampling variance;
                    mods = ~  bird_species,
                    random = list(~ 1 | paper_ID,
                                  ~ 1 | Observation_ID,
                                  ~ 1 | group_ID_coded,
                                  ~ 1 | population_ID,
                                  ~ 1 | bird_species),
                    method = "REML",
                  test = "t",
                  control = list(optimizer="optim"),
                  data = dataset_SMDH)

# Saving the model
saveRDS(SMDH_birds_pc, file = here::here("model/SMDH_birds_pc.rds"))

#----------------------------------------------------------------------------------
# Type of trait studied
#----------------------------------------------------------------------------------

lnRR_trait_pc <-
  metafor::rma.mv(yi = lnRR_sign, # specify lnRR as the effect size measure;
                    V = VCV_lnRR,# specify lnRR's sampling variance;
                    mods = ~ trait_type,
                    random = list(~ 1 | paper_ID,
                                  ~ 1 | Observation_ID,
                                  ~ 1 | group_ID_coded,
                                  ~ 1 | population_ID,
                                  ~ 1 | bird_species),
                    method = "REML",
                  test = "t",
                  control = list(optimizer="optim"),
                  data = dataset_lnRR)

# Saving the model
saveRDS(lnRR_trait_pc, file = here::here("model/lnRR_trait_pc.rds"))

SMDH_trait_pc <-
  metafor::rma.mv(yi = SMDH_sign, # specify lnRR as the effect size measure;
                    V = VCV_SMDH,# specify lnRR's sampling variance;
                    mods = ~ trait_type,
                    random = list(~ 1 | paper_ID,
                                  ~ 1 | Observation_ID,
                                  ~ 1 | group_ID_coded,
                                  ~ 1 | population_ID,
                                  ~ 1 | bird_species),
                    method = "REML",
                  test = "t",
                  control = list(optimizer="optim"),
                  data = dataset_SMDH)

# Saving the model
saveRDS(SMDH_trait_pc, file = here::here("model/SMDH_trait_pc.rds"))

\

### 2025-07-09 code/08_figures-tables.Rmd
No build, pushing to switch machines :D

# ---- FIGURES ————–

@@

# To add the zoomed in map.. to show the points more clearly
zoom_map <- ggplot() + 
  geom_map(data = world_coordinates, map = world_coordinates,
           aes(map_id = region),
           color = "white", fill = "#D4D4D4") +
  geom_point(data = dataset_analysis_unique_rows,
             aes(x = Long_Location, y = Lat_Location,
                 size = size.freq, colour = bird_species),
             alpha = 0.6) +
  scale_size(range = c(1, 2)) +
  scale_colour_manual(values = c("#00B0BE","#FFB255",  "#FF8CAE", 
                                 "#F47A00", "#98C127","#003A7D","#7E4794")) +
  coord_cartesian(xlim = c(-120, 120), ylim = c(25, 65)) +  # Northern Hemisphere
  theme_void() +
  theme(
    legend.position = "none",
    plot.background = element_rect(color = "white", fill="white"),
    panel.border = element_rect(colour = "black", fill = NA, size = 1)
  )

geographic_distribution <- ggdraw() +
  draw_plot(fig_map) +
  draw_plot(zoom_map, x = 0.10, y = 0.12, width = 0.52, height = 0.22) + theme(panel.border = element_rect(colour = "black", fill=NA, size=1.5))

@@

# Plot for lnRR
intercept_lnRR_plot <- orchaRd::orchard_plot(intercept_lnRR,
                                    mod = "1",
                                    group = "paper_ID",
                                    trunk.size = 0.25,
                                    branch.size = 2,
                                    twig.size = 0.5,
                                    alpha = 0.2,
                                    xlab = "Effect size (Log Response Ratio- lnRR)",
                                    fill = T) +
   scale_fill_manual(values = "#98C127") +
   scale_colour_manual(values = "#98C127" ) +
  theme_minimal(base_size = 14) +
  theme(
    panel.border = element_rect(colour = "black", fill = NA, size = 0.8),
    legend.position = c(0.98, 0.05),
    legend.justification = c(1, 0),
    legend.direction = "horizontal",
    legend.title = element_text(size = 7),
    legend.text = element_text(size = 7),
    axis.title = element_text(size = 10),
    axis.text.x = element_text(size = 10),
    axis.text.y = element_blank()
  ) +
  labs(x = "Intercept")

# Plot for SMDH
intercept_SMDH_plot <- orchaRd::orchard_plot(intercept_SMDH,
                                    mod = "1",
                                    group = "paper_ID",
                                    trunk.size = 0.25,
                                    branch.size = 2,
                                    twig.size = 0.5,
                                    alpha = 0.2,
                                    xlab = "Effect size (Standardized Mean Difference- SMD(H))",
                                    fill = TRUE) +
  scale_fill_manual(values = "#F47A00") +
  scale_colour_manual(values = "#F47A00") +
  theme_minimal(base_size = 14) +
  theme(
    panel.border = element_rect(colour = "black", fill = NA, size = 0.8),
    legend.position = c(0.98, 0.05),
    legend.justification = c(1, 0), 
    legend.direction = "horizontal",
    legend.title = element_text(size = 7),
    legend.text = element_text(size = 7),
    axis.title = element_text(size = 10),
    axis.text.x = element_text(size = 10),
    axis.text.y = element_blank()
  ) +
  labs(x = "Intercept")

@@

ggsave(here::here("figures/Figure_overall_effect.png"), plot = Figure_intercept, height = 150, width = 170, units = "mm", dpi = 600)
```

@@

lnRR_hypothesis_plot <-
  orchard_plot(mod_results(lnRR_hypothesis,
                           mod = "Hypothesis",
                           group = "paper_ID"),
               trunk.size = 0.25,
               branch.size = 1,
               twig.size = 0.5,
               alpha = 0.4,
               xlab ="") +
  scale_colour_manual(values = c("#FF8CAE", "#003A7D", "#7E4794")) +
  scale_fill_manual(values = c("#FF8CAE", "#003A7D", "#7E4794")) +
  labs(x = "",
       y = "lnRR")+
  theme(
    panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.8),
    legend.position.inside = c(0.99, 0.05),
    legend.justification = c(1, 0), 
    legend.direction = "horizontal",
    legend.title = element_text(size = 6),
    legend.text = element_text(size = 6),
    axis.title = element_text(size = 10),
    axis.text.x = element_text(size = 10),
    axis.text.y = element_text(angle = 90, vjust = 0.01, hjust = 0.5)
  )+ scale_x_discrete(labels = c("Both","Courtship","Parental Care"))

@@

SMDH_hypothesis_plot <-
  orchard_plot(
    mod_results(
      SMDH_hypothesis,
      mod = "Hypothesis",
      group = "paper_ID"
    ),
    trunk.size = 0.25,
    branch.size = 1,
    twig.size = 0.5,
    alpha = 0.4,
    xlab ="") +
  scale_colour_manual(values = c("#FF8CAE", "#003A7D", "#7E4794")) +
  scale_fill_manual(values = c("#FF8CAE", "#003A7D", "#7E4794")) +
  labs(x = "",
       y = "SMD(H)")+
    theme(
    panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.8),
    legend.position.inside = c(0.99, 0.05),
    legend.justification = c(1, 0), 
    legend.direction = "horizontal",
    legend.title = element_text(size = 6),
    legend.text = element_text(size = 6),
    axis.title = element_text(size = 10),
    axis.text.x = element_text(size = 10),
    axis.text.y = element_text(angle = 90, vjust = 0.8, hjust = 1)
  )+ scale_x_discrete(labels = c("Both","Courtship","Parental Care"))

@@

ggsave(here::here("figures/Figure_hypothesis.png"), plot = Figure_hypothesis, height = 120, width = 250, units = "mm", dpi = 600)
```

@@

# -------- TABLES ———-

>>>>

# ---- FIGURES --------------

@@

# To add the zoomed in map.. to show the points more clearly
zoom_map <- ggplot() + 
  geom_map(data = world_coordinates, map = world_coordinates,
           aes(map_id = region),
           color = "white", fill = "#D4D4D4") +
  geom_point(data = dataset_analysis_unique_rows,
             aes(x = Long_Location, y = Lat_Location,
                 size = size.freq, colour = bird_species),
             alpha = 0.9) +
  scale_size(range = c(2, 4)) +
  scale_colour_manual(values = c("#00B0BE","#FFB255",  "#FF8CAE", 
                                 "#F47A00", "#98C127","#003A7D","#7E4794")) +
  coord_cartesian(xlim = c(-10, 20), ylim = c(25, 65)) +  # Northern Hemisphere
  theme_void() +
  theme(
    legend.position = "none",
    plot.background = element_rect(color = "white", fill="white"),
    panel.border = element_rect(colour = "black", fill = NA, size = 1)
  )

geographic_distribution <- ggdraw() +
  draw_plot(fig_map) +
  draw_plot(zoom_map, x = 0.05, y = 0.15, width = 0.28, height = 0.38) + theme(panel.border = element_rect(colour = "black", fill=NA, size=1.5))

@@

# Plot for lnRR

intercept_lnRR_plot<- orchaRd::orchard_plot(intercept_lnRR,
                                             mod = "1",
                                             group = "paper_ID",
                                             trunk.size = 0.3,
                                             branch.size = 2,
                                             twig.size = 0.5,
                                             alpha = 0.2,
                                             xlab = "Effect size (lnRR)", 
                                             fill =  T) +
  scale_fill_manual(values = "#98C127") +
  scale_colour_manual(values = "#98C127" ) +
theme_minimal(base_size = 14) +
  theme(
    panel.border = element_rect(colour = "black", fill = NA, size = 0.8),
    legend.position = c(0.98, 0.05),
    legend.justification = c(1, 0),
    legend.direction = "horizontal",
    legend.title = element_text(size = 7),
    legend.text = element_text(size = 7),
    axis.title = element_text(size = 10),
    axis.text.x = element_text(size = 10),
    axis.text.y = element_blank()
  ) +
  labs(x = "Intercept")

# Plot for SMDH
intercept_SMDH_plot <- orchaRd::orchard_plot(intercept_SMDH,
                                    mod = "1",
                                    group = "paper_ID",
                                    trunk.size = 0.3,
                                    branch.size = 2,
                                    twig.size = 0.5,
                                    alpha = 0.2,
                                    xlab = "Effect size (SMDH)",
                                    fill = TRUE) +
  scale_fill_manual(values = "#F47A00") +
  scale_colour_manual(values = "#F47A00") +
  theme_minimal(base_size = 14) +
  theme(
    panel.border = element_rect(colour = "black", fill = NA, size = 0.8),
    legend.position = c(0.98, 0.05),
    legend.justification = c(1, 0), 
    legend.direction = "horizontal",
    legend.title = element_text(size = 7),
    legend.text = element_text(size = 7),
    axis.title = element_text(size = 10),
    axis.text.x = element_text(size = 10),
    axis.text.y = element_blank()
  ) +
  labs(x = "Intercept")

@@

ggsave(here::here("figures/Figure_overall_effect.png"), plot = Figure_intercept, height = 150, width = 170, units = "mm", dpi = 600)

###----------------------------------------------------------------------------------

## Now the cropped versions presented in the main manuscript..

###----------------------------------------------------------------------------------

intercept_lnRR_plot_crop <- orchaRd::orchard_plot(intercept_lnRR,
                                             mod = "1",
                                             group = "paper_ID",
                                             trunk.size = 0.5,
                                             branch.size = 2,
                                             twig.size = 0.5,
                                             alpha = 0.2,
                                             xlab = "Effect size (lnRR)", 
                                             fill =  T) +
  scale_fill_manual(values = "#98C127") +
  scale_colour_manual(values = "#98C127" ) +
    scale_y_continuous(limits = c(-0.7, 0.7)) +
theme_minimal(base_size = 14) +
  theme(
    panel.border = element_rect(colour = "black", fill = NA, size = 0.8),
    legend.position = c(0.98, 0.05),
    legend.justification = c(1, 0),
    legend.direction = "horizontal",
    legend.title = element_text(size = 7),
    legend.text = element_text(size = 7),
    axis.title = element_text(size = 10),
    axis.text.x = element_text(size = 10),
    axis.text.y = element_blank()
  ) +
  labs(x = "Intercept")

# Plot for SMDH
intercept_SMDH_plot_crop <- orchaRd::orchard_plot(intercept_SMDH,
                                    mod = "1",
                                    group = "paper_ID",
                                    trunk.size = 0.5,
                                    branch.size = 2,
                                    twig.size = 0.5,
                                    alpha = 0.2,
                                    xlab = "Effect size (SMDH)",
                                    fill = TRUE) +
  scale_fill_manual(values = "#F47A00") +
  scale_colour_manual(values = "#F47A00") +
  scale_y_continuous(limits = c(-2.7, 2.7)) +
  theme_minimal(base_size = 14) +
  theme(
    panel.border = element_rect(colour = "black", fill = NA, size = 0.8),
    legend.position = c(0.98, 0.05),
    legend.justification = c(1, 0), 
    legend.direction = "horizontal",
    legend.title = element_text(size = 7),
    legend.text = element_text(size = 7),
    axis.title = element_text(size = 10),
    axis.text.x = element_text(size = 10),
    axis.text.y = element_blank()
  ) +
  labs(x = "Intercept")

# Combine using patchwork
Figure_intercept_crop <- intercept_lnRR_plot_crop / intercept_SMDH_plot_crop +
  plot_annotation(tag_level = c("A","B"))

ggsave(here::here("figures/Figure_overall_effect_crop.png"), plot = Figure_intercept_crop, height = 150, width = 170, units = "mm", dpi = 600)
```

@@

lnRR_hypothesis_plot <-
  orchard_plot(mod_results(lnRR_hypothesis,
                           mod = "Hypothesis",
                           group = "paper_ID"),
               trunk.size = 0.25,
               branch.size = 1,
               twig.size = 0.5,
               alpha = 0.4,
               xlab ="") +
  scale_colour_manual(values = c("#FF8CAE", "#003A7D", "#7E4794")) +
  scale_fill_manual(values = c("#FF8CAE", "#003A7D", "#7E4794")) +
  labs(x = "",
       y = "Effect size (lnRR)")+
  theme(
    panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.8),
    legend.position.inside = c(0.99, 0.05),
    legend.justification = c(1, 0), 
    legend.direction = "horizontal",
    legend.title = element_text(size = 6),
    legend.text = element_text(size = 6),
    axis.title = element_text(size = 10),
    axis.text.x = element_text(size = 10),
    axis.text.y = element_text(angle = 0, vjust = 0.5, hjust = 1))+ 
  scale_x_discrete(labels = c("Both","Courtship","Parental Care"))

@@

SMDH_hypothesis_plot <-
  orchard_plot(
    mod_results(
      SMDH_hypothesis,
      mod = "Hypothesis",
      group = "paper_ID"
    ),
    trunk.size = 0.25,
    branch.size = 1,
    twig.size = 0.5,
    alpha = 0.4,
    xlab ="") +
  scale_colour_manual(values = c("#FF8CAE", "#003A7D", "#7E4794")) +
  scale_fill_manual(values = c("#FF8CAE", "#003A7D", "#7E4794")) +
  labs(x = "",
       y = "Effect size (SMDH)")+
    theme(
    panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.8),
    legend.position.inside = c(0.99, 0.05),
    legend.justification = c(1, 0), 
    legend.direction = "horizontal",
    legend.title = element_text(size = 6),
    legend.text = element_text(size = 6),
    axis.title = element_text(size = 10),
    axis.text.x = element_text(size = 10),
    axis.text.y = element_text(angle = 0, vjust = 0.5, hjust = 1))+ 
  scale_x_discrete(labels = c("Both","Courtship","Parental Care"))

@@

ggsave(here::here("figures/Figure_hypothesis.png"), plot = Figure_hypothesis, height = 120, width = 250, units = "mm", dpi = 600)

##-----------------------------------------------------------------------------

# Now the cropped figures for the main manuscript

##-----------------------------------------------------------------------------

lnRR_hypothesis_plot_crop <-
  orchard_plot(mod_results(lnRR_hypothesis,
                           mod = "Hypothesis",
                           group = "paper_ID"),
               trunk.size = 0.5,
               branch.size = 1.3,
               twig.size = 0.5,
               alpha = 0.4,
               fill = T,
               xlab ="") +
  scale_colour_manual(values = c("#FF8CAE", "#003A7D", "#7E4794")) +
  scale_fill_manual(values = c("#FF8CAE", "#003A7D", "#7E4794")) +
    scale_y_continuous(limits = c(-0.7, 0.7)) +
  labs(x = "",
       y = "Effect size (lnRR)")+
  theme(
    panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.8),
    legend.position.inside = c(0.99, 0.05),
    legend.justification = c(1, 0), 
    legend.direction = "horizontal",
    legend.title = element_text(size = 6),
    legend.text = element_text(size = 6),
    axis.title = element_text(size = 10),
    axis.text.x = element_text(size = 10),
    axis.text.y = element_text(angle = 0, vjust = 0.5, hjust = 1))+ 
  scale_x_discrete(labels = c("Both","Courtship","Parental\nCare"))

SMDH_hypothesis_plot_crop <-
  orchard_plot(
    mod_results(
      SMDH_hypothesis,
      mod = "Hypothesis",
      group = "paper_ID"
    ),
    trunk.size = 0.5,
    branch.size = 1.3,
    twig.size = 0.5,
    alpha = 0.4,
    fill = T,
    xlab ="") +
  scale_colour_manual(values = c("#FF8CAE", "#003A7D", "#7E4794")) +
  scale_fill_manual(values = c("#FF8CAE", "#003A7D", "#7E4794")) +
  scale_y_continuous(limits = c(-2.7, 2.7)) +
  labs(x = "",
       y = "Effect size (SMDH)")+
  theme(
    panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.8),
    legend.position.inside = c(0.99, 0.05),
    legend.justification = c(1, 0), 
    legend.direction = "horizontal",
    legend.title = element_text(size = 6),
    legend.text = element_text(size = 6),
    axis.title = element_text(size = 10),
    axis.text.x = element_text(size = 10),
    axis.text.y = element_text(angle = 0, vjust = 0.5, hjust = 1))+ 
  scale_x_discrete(labels = c("Both","Courtship","Parental\nCare"))

SMDH_hypothesis_plot_crop <- SMDH_hypothesis_plot_crop +
  theme(axis.text.y  = element_blank(),
        axis.title.y = element_blank(),
        axis.ticks.y = element_blank())

# Combine using patchwork
Figure_hypothesis_crop <- lnRR_hypothesis_plot_crop + SMDH_hypothesis_plot_crop +
  plot_annotation(tag_level = c("A","B"))

ggsave(here::here("figures/Figure_hypothesis_crop.png"), plot = Figure_hypothesis_crop, height = 120, width = 250, units = "mm", dpi = 600)
```

@@

# -------- TABLES ----------
